```latex
\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\title{Worksheet ? HUnit\_4-1\_Notes ? HUnit\_4-1\_Notes}
\author{}
\date{}

\begin{document}

\maketitle

\section*{Topic 1: Introduction to HUnit}
HUnit is a unit testing framework for Haskell, which allows developers to write and run tests. Unit testing helps ensure that individual components of a program work as intended.

\textbf{Explanatory Notes:}
- HUnit tests are written as functions that return a test case.
- Each test case can be grouped into test suites to run multiple tests together.

\textbf{Practice Problems:}
1. Write a simple HUnit test for a function that adds two numbers.
2. Create a test suite that includes tests for both addition and subtraction functions.

\section*{Topic 2: Writing Test Cases}
To write a test case in HUnit, you can use the `TestCase` function.

\textbf{Explanatory Notes:}
- Each test case should check for expected outcomes.
- Use assertions like `assertEqual` to verify results.

\textbf{Practice Problems:}
1. Write a test case that checks if the function `multiply` correctly multiplies two integers.
2. Create a test case that verifies the behavior of a function that returns the maximum of two numbers.

\section*{Topic 3: Running Tests}
Tests can be executed using the `runTestTT` function which runs all tests and reports the results.

\textbf{Explanatory Notes:}
- Running tests helps identify errors and ensure code quality.
- Review the output carefully to understand which tests passed or failed.

\textbf{Practice Problems:}
1. Write a function that runs a test suite containing three test cases.
2. Modify a failing test case to ensure it passes, then rerun the tests.

\section*{Answer Key}
1. 
```haskell
testAdd = TestCase (assertEqual "for (1+2)," 3 (add 1 2))
```
2. 
```haskell
testSuite = TestList [testAdd, testSubtract]
```
3. 
```haskell
main = runTestTT testSuite
```
4. 
```haskell
testMultiply = TestCase (assertEqual "for (3*2)," 6 (multiply 3 2))
```
5. 
```haskell
testMax = TestCase (assertEqual "for (3, 5)," 5 (max 3 5))
```

\end{document}
```